Calendar-based graphics for visualizing people's daily schedules

### 2019-11-21 calendar-vis.Rmd
minor tweaks

(ref:ped-map-cap) Google map of the Melbourne city area, grey dots indicate sensor locations. The three locations highlighted will be analyzed in the paper: the State Library is a public library; Flagstaff Station is a train station, closed on non-work days; Birrarung Marr is an outdoor park hosting many cultural and sports events.

@@

Then the final coordinates for making the calendar plots of the pedestrian sensor data is given by:
\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c.
  \end{aligned}
  (\#eq:final)
\end{equation}

>>>>

(ref:ped-map-cap) Google map of the Melbourne city area, gray dots indicate sensor locations. The three locations highlighted will be analyzed in the paper: the State Library is a public library; Flagstaff Station is a train station, closed on non-work days; Birrarung Marr is an outdoor park hosting many cultural and sports events.

@@

Then the final coordinates for making the calendar plots of the pedestrian sensor data are given by:
\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c.
  \end{aligned}
  (\#eq:final)
\end{equation}
